---
title: "IBM Den: Figure 2" 
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    highlight: kate
    code_folding: true 
    toc: true            
    toc_depth: 2         
editor_options: 
  chunk_output_type: console
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, 
                      retina = 1, dev = "ragg_png")
```


# Setup

```{r packages}
library(tidyverse)
library(patchwork)
library(ragg)
```


# Data

```{r data-prep}
output <- 
  readr::read_csv(
    here::here("data", "YBC_Continuous_Breeding continuous_breeding-table.csv"), 
    skip = 6
  ) %>% 
  janitor::clean_names() %>% 
  mutate(
    transmission = if_else(frequency_transmission == TRUE, "Frequency", "Density"),
    ext = if_else(ext == "extinct", 1, 0)
  ) %>% 
  #filter(rnot == 20) %>% 
  arrange(run_number) %>% 
  mutate(modularity = 0.10 / within_group_contact) %>% 
  as.data.frame()
```


## Estimates per Parameter

Estimate mean difference in epidemic fade-out between age-dependent and age-independent networks:

```{r data-immunity}
path <- here::here("data", "fig2_immunity.Rds")

if(!file.exists(path)){
  gridim <- data.frame(NULL)
  
  tabpar <-
    expand.grid(
      unique(output$"modularity"),
      unique(output$"infection_length"),
      unique(output$"virulence"),
      unique(output$"group_size"),
      unique(output$"fertility"),
      unique(output$"survival"),
      unique(output$"rnot"),
      unique(output$"transmission")
    )

  colnames(tabpar) <-
    c(
      "modularity",
      "infection_length",
      "virulence",
      "group_size",
      "fertility",
      "survival",
      "rnot",
      "transmission"
    )

  for (r in 1:nrow(tabpar)) {
    select <-
      subset(
        output,
        modularity == tabpar[r, "modularity"] &
          group_size == tabpar[r, "group_size"] &
          virulence == tabpar[r, "virulence"] &
          infection_length == tabpar[r, "infection_length"] &
          fertility == tabpar[r, "fertility"] &
          survival == tabpar[r, "survival"] &
          rnot == tabpar[r, "rnot"] &
          transmission == tabpar[r, "transmission"]
      )
    
    extinction <-
      aggregate(select[, "ext"], 
                list(immunity_barrier = select[, "immunity_barrier"]), sum)
    outof <-
      aggregate(select[, "ext"], 
                list(immunity_barrier = select[, "immunity_barrier"]), length)
    
    persistence <- outof - extinction
    
    b <- matrix(c(extinction$x, persistence$x), nrow = 2, 
                dimnames = list(immunity_barrier = extinction$immunity_barrier,
                                Persistence = c("NO", "YES")))
    
    Fisher <- fisher.test(b)
    
    if(Fisher$p.value < 0.05) {  
      gridim <-
        rbind(
          cbind(
            extinction,
            rep(Fisher$p.value, nrow(extinction)),
            rep(tabpar[r, "modularity"], nrow(extinction)),
            rep(tabpar[r, "infection_length"], nrow(extinction)),
            rep(tabpar[r, "virulence"], nrow(extinction)),
            rep(tabpar[r, "group_size"], nrow(extinction)), 
            rep(tabpar[r, "fertility"], nrow(extinction)), 
            rep(tabpar[r, "survival"], nrow(extinction)), 
            rep(tabpar[r, "rnot"], nrow(extinction)), 
            rep(tabpar[r, "transmission"], nrow(extinction))), gridim)
    }
  }
  
  colnames(gridim) = c("immunity",
                       "extinction",
                       "significant",
                       "modularity",
                       "infection_length",
                       "virulence",
                       "group_size",
                       "fertility",
                       "survival",
                       "rnot",
                       "transmission")
  
  immunity <- subset(gridim, immunity == 52)
  noimmunity <- subset(gridim, immunity == 1)
  immunity$difference <- (immunity$extinction - noimmunity$extinction) / 30
  
  saveRDS(immunity, path)
} else {
  immunity <- readRDS(path)
}
```

Estimate mean difference in epidemic fade-out between modular and none modular networks

```{r data-modularity}
path <- here::here("data", "fig2_modularity.Rds")

if(!file.exists(path)){
  gridim <- data.frame(NULL)
  
  tabpar <-
    expand.grid(
      unique(output$"immunity_barrier"),
      unique(output$"infection_length"),
      unique(output$"virulence"),
      unique(output$"group_size"),
      unique(output$"fertility"),
      unique(output$"survival"),
      unique(output$"rnot"),
      unique(output$"transmission")
    )

  colnames(tabpar) <- c("immunity_barrier",
                        "infection_length",
                        "virulence",
                        "group_size",
                        "fertility",
                        "survival",
                        "rnot",
                        "transmission")

  for (r in 1:nrow(tabpar)) {
    select <-
      subset(
        output,
        immunity_barrier == tabpar[r, "immunity_barrier"] &
        group_size == tabpar[r, "group_size"] &
        virulence == tabpar[r, "virulence"] &
        infection_length == tabpar[r, "infection_length"] &
        fertility == tabpar[r, "fertility"] &
        survival == tabpar[r, "survival"] &
        rnot == tabpar[r, "rnot"] &
        transmission == tabpar[r, "transmission"]
      )
    
    extinction <-
      aggregate(select[, "ext"], list(modularity =  select[, "modularity"]), sum)
    
    outof <-
      aggregate(select[, "ext"], list(modularity =  select[, "modularity"]), length)
    
    persistence <- outof - extinction
    
    b <- matrix(c(extinction$x, persistence$x), nrow = 3, 
                dimnames = list(Modularity = c(10, 50, 100), 
                                Persistence = c("NO", "YES")))
    
    Fisher <- fisher.test(b)
    
    if(Fisher$p.value < 0.05) {  
    gridim <-
      rbind(
        cbind(
          extinction,
          rep(Fisher$p.value, nrow(extinction)),
          rep(tabpar[r, "immunity_barrier"], nrow(extinction)),
          rep(tabpar[r, "infection_length"], nrow(extinction)),
          rep(tabpar[r, "virulence"], nrow(extinction)),
          rep(tabpar[r, "group_size"], nrow(extinction)), 
          rep(tabpar[r, "fertility"], nrow(extinction)), 
          rep(tabpar[r, "survival"], nrow(extinction)), 
          rep(tabpar[r, "rnot"], nrow(extinction)), 
          rep(tabpar[r, "transmission"], nrow(extinction))), gridim)
    }
  }
  
  colnames(gridim) = c("modularity",
                       "extinction",
                       "significant",
                       "immunity_barrier",
                       "infection_length",
                       "virulence",
                       "group_size",
                       "fertility",
                       "survival",
                       "rnot",
                       "transmission")
  
  modularity <- subset(gridim, modularity == 0.1)
  nomodularity <- subset(gridim, modularity == 1)
  modularity$diff <- (modularity$extinction - nomodularity$extinction) / 30

  saveRDS(modularity, path)
} else {
  modularity <- readRDS(path)
}
```

Estimate mean difference in epidemic fade-out between networks with high and low survival:

```{r data-survival}
path <- here::here("data", "fig2_survival.Rds")

if(!file.exists(path)){
  gridim <- data.frame(NULL)
  
  tabpar <-
    expand.grid(
      unique(output$"immunity_barrier"),
      unique(output$"infection_length"),
      unique(output$"virulence"),
      unique(output$"group_size"),
      unique(output$"fertility"),
      unique(output$"modularity"),
      unique(output$"rnot"),
      unique(output$"transmission")
    )

  colnames(tabpar) <- c("immunity_barrier",
                        "infection_length",
                        "virulence",
                        "group_size",
                        "fertility",
                        "modularity",
                        "rnot",
                        "transmission")

  for (r in 1:nrow(tabpar)) {
    select <-
      subset(
        output,
        immunity_barrier == tabpar[r, "immunity_barrier"] &
          group_size == tabpar[r, "group_size"] &
          virulence == tabpar[r, "virulence"] &
          infection_length == tabpar[r, "infection_length"] &
          fertility == tabpar[r, "fertility"] &
          modularity == tabpar[r, "modularity"] &
          rnot == tabpar[r, "rnot"] &
          transmission == tabpar[r, "transmission"]
      )
    
    extinction <-
      aggregate(select[, "ext"], list(survial =  select[, "survival"]), sum)
    
    outof <-
      aggregate(select[, "ext"], list(survival =  select[, "survival"]), length)
    
    persistence <- outof - extinction
    
    b <- matrix(c(extinction$x, persistence$x), nrow = 3, 
                dimnames = list(survival = extinction$survival, 
                                Persistence = c("NO", "YES")))
    
    Fisher <- fisher.test(b)
    
    if(Fisher$p.value < 0.05) {  
      gridim <-
        rbind(
          cbind(
            extinction,
            rep(Fisher$p.value, nrow(extinction)),
            rep(tabpar[r, "immunity_barrier"], nrow(extinction)),
            rep(tabpar[r, "infection_length"], nrow(extinction)),
            rep(tabpar[r, "virulence"], nrow(extinction)),
            rep(tabpar[r, "group_size"], nrow(extinction)),  
            rep(tabpar[r, "fertility"], nrow(extinction)), 
            rep(tabpar[r, "modularity"], nrow(extinction)), 
            rep(tabpar[r, "rnot"], nrow(extinction)), 
            rep(tabpar[r, "transmission"], nrow(extinction))), gridim)
    }
  }
  
  colnames(gridim) = c("survival",
                       "extinction",
                       "significant",
                       "immunity_barrier",
                       "infection_length",
                       "virulence",
                       "group_size",
                       "fertility",
                       "modularity",
                       "rnot",
                       "transmission")
  
  survival <- subset(gridim, survival == 0.9)
  lowsurv <- subset(gridim, survival == 0.6)
  survival$diff <- (survival$extinction - lowsurv$extinction) / 30  
  
  saveRDS(survival, path)
} else {
  survival <- readRDS(path)
}
```

Estimate mean difference in epidemic fade-out between networks with large and small group size:

```{r data-groupsize}
path <- here::here("data", "fig2_groupsize.Rds")

if(!file.exists(path)){
  gridim <- data.frame(NULL)
  
  tabpar <-
    expand.grid(
      unique(output$"immunity_barrier"),
      unique(output$"infection_length"),
      unique(output$"virulence"),
      unique(output$"survival"),
      unique(output$"fertility"),
      unique(output$"modularity"),
      unique(output$"rnot"),
      unique(output$"transmission")
    )

  colnames(tabpar) <- c("immunity_barrier",
                        "infection_length",
                        "virulence",
                        "survival",
                        "fertility",
                        "modularity",
                        "rnot",
                        "transmission")

  for (r in 1:nrow(tabpar)) {
    select <-
      subset(
        output,
          immunity_barrier == tabpar[r, "immunity_barrier"] &
          modularity == tabpar[r, "modularity"] &
          virulence == tabpar[r, "virulence"] &
          infection_length == tabpar[r, "infection_length"] &
          fertility == tabpar[r, "fertility"] &
          survival == tabpar[r, "survival"] &
          rnot == tabpar[r, "rnot"] &
          transmission == tabpar[r, "transmission"]
      )
    
    extinction <-
      aggregate(select[, "ext"], list(group_size = select[, "group_size"]), sum)
    
    outof <-
      aggregate(select[, "ext"], list(group_size =  select[, "group_size"]), length)
    
    persistence <- outof - extinction
    
    b <- matrix(c(extinction$x, persistence$x), nrow = 3, 
                dimnames = list(group_size = extinction$group_size, 
                                Persistence = c("NO", "YES")))
    
    Fisher <- fisher.test(b)
    
    if(Fisher$p.value < 0.05) {  
      gridim <-
        rbind(
          cbind(
            extinction,
            rep(Fisher$p.value, nrow(extinction)),
            rep(tabpar[r, "immunity_barrier"], nrow(extinction)),
            rep(tabpar[r, "infection_length"], nrow(extinction)),
            rep(tabpar[r, "virulence"], nrow(extinction)),
            rep(tabpar[r, "modularity"], nrow(extinction)), 
            rep(tabpar[r, "survival"], nrow(extinction)), 
            rep(tabpar[r, "fertility"], nrow(extinction)), 
            rep(tabpar[r, "rnot"], nrow(extinction)), 
            rep(tabpar[r, "transmission"], nrow(extinction))), gridim)
      }
  }
  
  colnames(gridim) = c("group_size",
                       "extinction",
                       "significant",
                       "immunity_barrier",
                       "infection_length",
                       "virulence",
                       "modularity",
                       "survival",
                       "fertility",
                       "rnot",
                       "transmission")
  
  gpsize <- subset(gridim, group_size == 100)
  smallgp <- subset(gridim, group_size == 10)
  gpsize$diff <- (gpsize$extinction - smallgp$extinction) / 30
  
  saveRDS(gpsize, path)
} else {
  gpsize <- readRDS(path)
}
```

Estimate mean difference in epidemic fade-out between networks with different infection lengths:

```{r data-infection}
path <- here::here("data", "fig2_infection.Rds")

if(!file.exists(path)){
  gridim <- data.frame(NULL)
  
  tabpar <-
    expand.grid(
      unique(output$"immunity_barrier"),
      unique(output$"group_size"),
      unique(output$"virulence"),
      unique(output$"survival"),
      unique(output$"fertility"),
      unique(output$"modularity"),
      unique(output$"rnot"),
      unique(output$"transmission")
    )

  colnames(tabpar) <- c("immunity_barrier",
                        "group_size",
                        "virulence",
                        "survival",
                        "fertility",
                        "modularity",
                        "rnot",
                        "transmission")

  for (r in 1:nrow(tabpar)) {
    select <-
      subset(
        output,
        immunity_barrier == tabpar[r, "immunity_barrier"] &
          modularity == tabpar[r, "modularity"] &
          virulence == tabpar[r, "virulence"] &
          group_size == tabpar[r, "group_size"] &
          fertility == tabpar[r, "fertility"] &
          survival == tabpar[r, "survival"] &
          rnot == tabpar[r, "rnot"] &
          transmission == tabpar[r, "transmission"]
      )
    
    extinction <-
      aggregate(select[, "ext"], list(infection_length =  select[, "infection_length"]), sum)
    outof <-
      aggregate(select[, "ext"], list(infection_length =  select[, "infection_length"]), length)
    persistence<-outof - extinction
    b <- matrix(c(extinction$x, persistence$x), nrow = 3, 
                dimnames = list(infection_length = extinction$infection_length,
                                Persistence = c("NO", "YES")))
    
    Fisher <- fisher.test(b)
    
    if(Fisher$p.value < 0.05) {  
      gridim <-
        rbind(
          cbind(
            extinction,
            rep(Fisher$p.value, nrow(extinction)),
            rep(tabpar[r, "immunity_barrier"], nrow(extinction)),
            rep(tabpar[r, "group_size"], nrow(extinction)),
            rep(tabpar[r, "virulence"], nrow(extinction)),
            rep(tabpar[r, "modularity"], nrow(extinction)), 
            rep(tabpar[r, "survival"], nrow(extinction)), 
            rep(tabpar[r, "fertility"], nrow(extinction)), 
            rep(tabpar[r, "rnot"], nrow(extinction)), 
            rep(tabpar[r, "transmission"], nrow(extinction))), gridim)
    }
  }

  colnames(gridim) = c("infection_length",
                       "extinction",
                       "significant",
                       "immunity_barrier",
                       "group_size",
                       "virulence",
                       "modularity",
                       "survival",
                       "fertility",
                       "rnot",
                       "transmission")
  
  infection <- subset(gridim, infection_length == 30)
  lowinfec <- subset(gridim, infection_length == 10)
  infection$diff <- (infection$extinction - lowinfec$extinction) / 30
  
  saveRDS(infection, path)

} else {
  infection <- readRDS(path)
}
```

Estimate mean difference in epidemic fade-out between networks with high and low virulence:

```{r data-virulence}
path <- here::here("data", "fig2_virulence.Rds")

if(!file.exists(path)){
  gridim <- data.frame(NULL)

  tabpar <-
    expand.grid(
      unique(output$"immunity_barrier"),
      unique(output$"group_size"),
      unique(output$"infection_length"),
      unique(output$"survival"),
      unique(output$"fertility"),
      unique(output$"modularity"),
      unique(output$"rnot"),
      unique(output$"transmission")
    )

  colnames(tabpar) <- c("immunity_barrier",
                        "group_size",
                        "infection_length",
                        "survival",
                        "fertility",
                        "modularity",
                        "rnot",
                        "transmission")

  for (r in 1:nrow(tabpar)) {
    select <-
      subset(
        output,
        immunity_barrier == tabpar[r, "immunity_barrier"] &
          modularity == tabpar[r, "modularity"] &
          infection_length == tabpar[r, "infection_length"] &
          group_size == tabpar[r, "group_size"] &
          fertility == tabpar[r, "fertility"] &
          survival == tabpar[r, "survival"] &
          rnot == tabpar[r, "rnot"] &
          transmission == tabpar[r, "transmission"]
      )
    
    extinction <-
      aggregate(select[, "ext"], list(virulence =  select[, "virulence"]), sum)
    
    outof <-
      aggregate(select[, "ext"], list(virulence =  select[, "virulence"]), length)
    
    persistence <- outof - extinction
    
    b <- matrix(c(extinction$x, persistence$x), nrow = 3, 
                dimnames = list(virulence = extinction$virulence, 
                                Persistence = c("NO", "YES")))
    
    Fisher <- fisher.test(b)
    
    if(Fisher$p.value < 0.05) {  
      gridim <-
        rbind(cbind(
          extinction,
          rep(Fisher$p.value, nrow(extinction))),
          gridim)
    }
  }
  
  colnames(gridim)[c(1,2)] = c(
    "virulence",
    "extinction")
  
  virulent <- subset(gridim, virulence == max(gridim$virulence))
  avirulent <- subset(gridim, virulence == min(gridim$virulence))
  virulent$diff <- (virulent$extinction - avirulent$extinction) / 30
  
  saveRDS(virulent, path)
  
} else {
  virulent <- readRDS(path)
}
```

Estimate mean difference selein epidemic fade-out between networks with different fertility rates:

```{r data-fertility}
path <- here::here("data", "fig2_fertility.Rds")

if(!file.exists(path)){
  gridim <- data.frame(NULL)

  tabpar <-
    expand.grid(
      unique(output$"immunity_barrier"),
      unique(output$"group_size"),
      unique(output$"infection_length"),
      unique(output$"survival"),
      unique(output$"virulence"),
      unique(output$"modularity"),
      unique(output$"rnot"),
      unique(output$"transmission")
    )

  colnames(tabpar) <- c("immunity_barrier",
                        "group_size",
                        "infection_length",
                        "survival",
                        "virulence",
                        "modularity",
                        "rnot",
                        "transmission")

  for (r in 1:nrow(tabpar)) {
    select <-
      subset(
        output,
        immunity_barrier == tabpar[r, "immunity_barrier"] &
          modularity == tabpar[r, "modularity"] &
          infection_length == tabpar[r, "infection_length"] &
          group_size == tabpar[r, "group_size"] &
          virulence == tabpar[r, "virulence"] &
          survival == tabpar[r, "survival"] &
          rnot == tabpar[r, "rnot"] &
          transmission == tabpar[r, "transmission"]
      )
    
    extinction <-
      aggregate(select[, "ext"], list(fertility =  select[, "fertility"]), sum)
    
    outof <-
      aggregate(select[, "ext"], list(fertility =  select[, "fertility"]), length)
    
    persistence <- outof - extinction
    
    b <- matrix(c(extinction$x, persistence$x), nrow = 3, 
                dimnames = list(fertility = extinction$fertility, 
                                Persistence = c("NO", "YES")))
    
    Fisher <- fisher.test(b)
    
    if(Fisher$p.value < 0.05) {  
      gridim <-
        rbind(cbind(
            extinction,
            rep(Fisher$p.value, nrow(extinction))),
            gridim)
    }
  }
  
  colnames(gridim)[c(1,2)] = c(
    "fertility",
    "extinction")
  
  fertile <- subset(gridim, fertility == max(gridim$fertility))
  sterile <- subset(gridim, fertility == min(gridim$fertility))
  fertile$diff <- (fertile$extinction - sterile$extinction) / 30
  
  saveRDS(fertile, path)
} else {
  fertile <- readRDS(path)
}
```

Estimate mean difference in epidemic fade-out between networks with differen transmission modes:

```{r data-transmission}
path <- here::here("data", "fig2_transmission.Rds")

if(!file.exists(path)){
  gridim <- data.frame(NULL)

  tabpar <-
    expand.grid(
      unique(output$"immunity_barrier"),
      unique(output$"group_size"),
      unique(output$"infection_length"),
      unique(output$"survival"),
      unique(output$"fertility"),
      unique(output$"modularity"),
      unique(output$"rnot"),
      unique(output$"virulence")
    )

  colnames(tabpar) <- c("immunity_barrier",
                        "group_size",
                        "infection_length",
                        "survival",
                        "fertility",
                        "modularity",
                        "rnot",
                        "virulence")

  for (r in 1:nrow(tabpar)) {
    select <-
      subset(
        output,
        immunity_barrier == tabpar[r, "immunity_barrier"] &
          modularity == tabpar[r, "modularity"] &
          infection_length == tabpar[r, "infection_length"] &
          group_size == tabpar[r, "group_size"] &
          virulence == tabpar[r, "virulence"] &
          survival == tabpar[r, "survival"] &
          rnot == tabpar[r, "rnot"] &
          fertility == tabpar[r, "fertility"]
      )
    
    extinction <-
      aggregate(select[, "ext"], list(transmission =  select[, "transmission"]), sum)
    outof <- c(30,30)
    
    persistence <- outof - extinction$x
    
    b <- matrix(c(extinction$x, persistence), nrow = 2, 
                dimnames = list(transmission = extinction$transmission, 
                                Persistence = c("NO", "YES")))
    
    Fisher <- fisher.test(b)
    
    if(Fisher$p.value < 0.05) {  
      gridim <-
        rbind(cbind(
          extinction,
          rep(Fisher$p.value, nrow(extinction))),
          gridim)
    }
  }
  
  colnames(gridim)[c(1,2)] = c(
    "transmission",
    "extinction")

  frequency <- subset(gridim, transmission == "Frequency")
  ddp <- subset(gridim, transmission == "Density")
  frequency$diff <- (frequency$extinction - ddp$extinction) / 30
  
  saveRDS(frequency, path)
} else {
  frequency <- readRDS(path)
}
```


## Combine All Estimates

```{r data-combine-all-vars}
path <- here::here("data", "fig2_allvars.Rds")

if(!file.exists(path)){
  fulldata <- 
    rbind(
      cbind(modularity$diff, rep("Contact ratio", length(modularity$diff))),
      cbind(gpsize$diff, rep("Group size", length(gpsize$diff))), 
      cbind(survival$diff, rep("Survival", length(survival$diff))),   
      cbind(fertile$diff, rep("Fertility", length(fertile$diff))), 
      cbind(infection$diff, rep("Infection length", length(infection$diff))),
      cbind(virulent$diff, rep("Virulence", length(virulent$diff))), 
      cbind(frequency$diff, rep("Transmission type", length(frequency$diff))), 
      cbind(immunity$diff, rep("Age at first between-group contact", length(immunity$diff))))
  
  colnames(fulldata) <- c("diff", "parameter")
  fulldata <- as.data.frame(fulldata)
  fulldata$diff <- as.numeric(as.character(fulldata$diff))
  fulldata$parameter <- as.character(fulldata$parameter)
  fulldata$type <- ifelse(
    fulldata$parameter %in% c("Infection length", "Virulence", "Transmission type"), 
    "viral", "host"
  )
  
  saveRDS(fulldata, path)
} else {
  fulldata <- readRDS(path)
}
```



# Figure

```{r plot, fig.width=16, fig.height=11}
theme_custom <-
  theme_classic(base_size = 18, base_family = "Times New Roman") +
  theme(axis.title.x = element_text(size = 17, margin = margin(t = 15)),
        axis.title.y = element_text(size = 17, margin = margin(r = 8)),
        axis.text = element_text(size = 14),
        axis.ticks = element_line(size = .8), 
        axis.ticks.length = unit(.2, "cm"),
        axis.line = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA, 
                                    size = 1.3),
        strip.background = element_rect(colour = "black", 
                                        fill = NA, size = 1.3),
        strip.text = element_text(size = 17, face = "bold", 
                                  margin = margin(10, 0, 10, 0)),
        panel.spacing.x = unit(1.3, "lines"),
        panel.spacing.y = unit(.8, "lines"),
        plot.title = element_text(face = "bold", size = 24, 
                                  margin = margin(0, 0, 10, 0)),
        plot.tag = element_text(size = 24))

p_viral <- 
  fulldata %>%  
  filter(type == "viral") %>% 
  ggplot(aes(diff)) +
    geom_histogram(
      fill = "#efa253",
      color = colorspace::darken("#efa253", .4),
      binwidth = .25,
      size = 1.1
    ) +
    geom_vline(
      xintercept = 0,
      linetype = "dashed",
      color = "#a00101", 
      size = .8
    ) +
    scale_x_continuous(
      expand = c(.025, .025),
      limits = c(-1.5, 2),
      breaks = seq(-1.5, 2, by = 0.5)
    ) +
    scale_y_continuous(
      expand = c(.035, .035),
      limits = c(0, 1100),
      breaks = seq(0, 1000 , by = 250)
    ) +
    facet_wrap(~parameter) +
    labs(
      x = NULL,
      y = "Count",
      title = "Pathogen-related traits",
      tag = expression(paste("(", italic("a"), ")"))
    ) +
    theme_custom

p_host <- 
  fulldata %>%
  filter(type == "host") %>% 
  ggplot(aes(diff)) +
    geom_histogram(
      fill = "#1a8775",
      color = colorspace::darken("#1a8775", .4),
      binwidth = .25,
      size = 1.1
    ) +
    geom_vline(
      xintercept = 0,
      linetype = "dashed",
      color = "#a00101",
      size = .8
    ) +
    scale_x_continuous(
      expand = c(.025, .025),
      limits = c(-1.5, 2),
      breaks = seq(-1.5, 2, by = 0.5)
    ) +
    scale_y_continuous(
      expand = c(.035, .035),
      limits = c(0, 550),
      breaks = seq(0, 500, by = 100)
    ) +
    facet_wrap(~parameter) +
    labs(
      x = "Difference in fade-out probabilities",
      y = "Count",
      title = "Host-related traits",
      tag =  expression(paste("(", italic("b"), ")"))
    ) +
    theme_custom

p_viral / p_host + plot_layout(heights = c(.43, 1)) 

ggsave(here::here("figures", "fig_2.pdf"), width = 16, height = 11, device = cairo_pdf)
```

***
  
<details><summary>Session Info</summary>
  
```{r sessionInfo}
## DO NOT REMOVE!
Sys.time()
#git2r::repository() ## uncomment if you are using GitHub
sessionInfo()
```

</details>
  
